Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-08 semiring.tex
Philippe semirings + labels

%%% semiring properties used in paper
% - commutative
% - bounded (implies idempotent and superior)
% - total
% - complete

>>>>

\begin{example}
The recursive subdivision of time that leads to hierarchichal
structures of music notation can be modeled as
production rules. Since there exists several possible division,
rules can be weighted 
in the tropical semiring whose domain $\mathbb{R}_+ \cup \{ +\infty\}$,
$\oplus$ is min, $\zero = +\infty$, $\otimes$ is sum, and $\one = 0$.
For instance, the following production rules define two possible divisions
of a bounded time interval into respectively a duplet and a triplet.
\[
\rho_1: q_0 \xrightarrow{0.06} \< q_{1}, q_{2}>,\
\rho_2: q_0 \xrightarrow{0.12} \< q_{1}, q_{2}, q_{2}>.
\]
\endex
\end{example}
%%% semiring properties used in paper
% - commutative
% - bounded (implies idempotent and superior)
% - total
% - complete
